---
title: "681FINALPROJECT"
author: "Kiara Zhang"
date: "2025-04-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(tidyverse)
library(lme4)
# install.packages("broom.mixed")
library(broom.mixed)
library(emmeans)
library(ggplot2)
library(dplyr)

```

```{r}
# load the data
df <- read.csv("cleaned_data.csv")
```

```{r}
# pivot the data longer
# add a variable 'time' = (0,6,12)
cols_to_convert <- c(
  "MRP_0", "MRP_6", "MRP_12",
  "Undertreat_0", "Undertreat_6", "Undertreat_12",
  "Sub_dose_0", "Sub_dose_6", "Sub_dose_12",
  "Med_Mon_0", "Med_Mon_6", "Med_Mon_12",
  "Sub_drug_0", "Sub_drug_6", "Sub_drug_12",
  "AE_0", "AE_6", "AE_12",
  "NonAd_0", "NonAd_6", "NonAd_12"
)

long_df <- df %>%
  pivot_longer(
    cols = all_of(cols_to_convert),
    names_to = c(".value", "time"),
    names_pattern = "(.+)_(\\d+)$"
  ) %>%
  mutate(
    time = as.numeric(time),
    Treatment = factor(Treatment),
    race = factor(race),
    site = factor(site)
  )

# view the data
glimpse(long_df)
head(long_df)

```

```{r}
# baseline as variables
baseline_subtypes <- df %>%
  select(ID, MRP_0, Undertreat_0, Sub_dose_0, Med_Mon_0, Sub_drug_0, AE_0, NonAd_0) %>%
  distinct()

long_df <- long_df %>%
  left_join(baseline_subtypes, by = "ID")
head(long_df)
```

## 8.4.1 Rate ratio of total MRPs (as a supplement to the primary analysis)
```{r}
# factor variables
long_df_analysis <- long_df %>%
  mutate(
    time = factor(time, levels = c(0, 6, 12)),
    Treatment = factor(Treatment, levels = c("Standard Care", "iMAP"))
  )

```

```{r}
# run poisson GLMM
model_mrp_rr <- glmer(
  MRP ~ Treatment * time + site + race + MRP_0 + (1 | ID),
  data = long_df_analysis,
  family = poisson(link = "log")
)

```

```{r}
# Extract fixed effect estimates from the fitted model
coefs <- fixef(model_mrp_rr)

# Extract the covariance matrix of fixed effects (for variance calculations)
vcov_mat <- vcov(model_mrp_rr)

# Get estimates of key coefficients
# β1: main effect of iMAP at baseline (time = 0)
# β4: interaction between iMAP and time = 6 months
# β5: interaction between iMAP and time = 12 months
beta1 <- coefs["TreatmentiMAP"]
beta4 <- coefs["TreatmentiMAP:time6"]
beta5 <- coefs["TreatmentiMAP:time12"]

# Calculate rate ratios (RR) using the exponentiated sum of coefficients
RR_6m <- exp(beta1 + beta4)
RR_12m <- exp(beta1 + beta5)

# --- Compute standard errors using the delta method ---
# SE for (β1 + β4)
se_6m <- sqrt(
  vcov_mat["TreatmentiMAP", "TreatmentiMAP"] +
  vcov_mat["TreatmentiMAP:time6", "TreatmentiMAP:time6"] +
  2 * vcov_mat["TreatmentiMAP", "TreatmentiMAP:time6"]
)

# SE for (β1 + β5)
se_12m <- sqrt(
  vcov_mat["TreatmentiMAP", "TreatmentiMAP"] +
  vcov_mat["TreatmentiMAP:time12", "TreatmentiMAP:time12"] +
  2 * vcov_mat["TreatmentiMAP", "TreatmentiMAP:time12"]
)

# --- Compute 95% Confidence Intervals (CI) ---
# CI = exp((β1 + βx) ± 1.96 * SE)
CI_6m <- exp(c((beta1 + beta4) - 1.96 * se_6m,
               (beta1 + beta4) + 1.96 * se_6m))

CI_12m <- exp(c((beta1 + beta5) - 1.96 * se_12m,
                (beta1 + beta5) + 1.96 * se_12m))

# --- Compute Wald z statistics ---
z_6m <- (beta1 + beta4) / se_6m
z_12m <- (beta1 + beta5) / se_12m

# --- Compute two-sided p-values for the Wald test ---
p_6m <- 2 * (1 - pnorm(abs(z_6m)))
p_12m <- 2 * (1 - pnorm(abs(z_12m)))

# --- Output the results as a named list ---
list(
  RR_6m = RR_6m,
  CI_6m = CI_6m,
  z_6m = z_6m,
  p_6m = p_6m,
  
  RR_12m = RR_12m,
  CI_12m = CI_12m,
  z_12m = z_12m,
  p_12m = p_12m
)
```


```{r}
# Plot the result
rr_data <- data.frame(
  Time = c("6 Months", "12 Months"),
  RR = c(0.8743, 0.7814),
  CI_lower = c(0.7896, 0.7052),
  CI_upper = c(0.9680, 0.8658)
)

ggplot(rr_data, aes(x = Time, y = RR)) +
  geom_point(size = 3, color = "blue") +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2, color = "gray40") +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  coord_flip() +
  ylim(0.6, 1.1) +
  labs(
    title = "Rate Ratio of Total MRPs (iMAP vs. Standard Care)",
    y = "Rate Ratio (RR)", x = ""
  ) +
  theme_minimal(base_size = 13)

```


To evaluate the impact of the iMAP intervention on the rate of total medication-related problems (MRPs), we fit a Poisson generalized linear mixed model adjusting for race, site, and baseline MRP count.

At 6 months, participants in the iMAP group had a significantly lower rate of MRPs compared to those in the standard care group, with a rate ratio (RR) of 0.87 (95% CI: 0.79–0.97, p = 0.0097).

At 12 months, the effect was even stronger, with the iMAP group showing a RR of 0.78 (95% CI: 0.71–0.87, p < 0.0001), indicating a 22% reduction in MRP rate relative to standard care.

These results suggest that the iMAP intervention substantially reduced medication-related problems over time compared to standard care.

## 8.4.2	Analysis of Secondary Outcome: Subgroup of MRPs

```{r}
#view the number of events of each subgroup
df_sub <- long_df %>%
  filter(time %in% c(6, 12))

subgroups <- c("Undertreat", "Sub_dose", "Med_Mon", "Sub_drug", "AE", "NonAd")

subgroup_counts <- sapply(subgroups, function(var) {
  df_sub %>% filter(.data[[var]] == 1) %>% pull(ID) %>% unique() %>% length()
})

subgroup_counts_df <- data.frame(
  Subgroup = names(subgroup_counts),
  N_with_event = as.vector(subgroup_counts)
)

print(subgroup_counts_df)
```

### Suboptimal dosing modeling
```{r}
model_subdose <- glmer(
  Sub_dose ~ Treatment * time + site + race + Sub_dose_0 + (1 | ID),
  data = long_df_analysis,
  family = binomial(link = "logit")
)

summary(model_subdose)
```

```{r}
# Extract fixed effects (log-odds coefficients)
coefs <- fixef(model_subdose)

# Extract the variance-covariance matrix of fixed effects
vcov_mat <- vcov(model_subdose)

# --- Pull key coefficients ---
# β1: main effect of iMAP at baseline
beta1 <- coefs["TreatmentiMAP"]

# β4: interaction of iMAP × time = 6 months
beta4 <- coefs["TreatmentiMAP:time6"]

# β5: interaction of iMAP × time = 12 months
beta5 <- coefs["TreatmentiMAP:time12"]

# --- Compute standard errors using the delta method ---
# SE for (β1 + β4)
se_6 <- sqrt(
  vcov_mat["TreatmentiMAP", "TreatmentiMAP"] +
  vcov_mat["TreatmentiMAP:time6", "TreatmentiMAP:time6"] +
  2 * vcov_mat["TreatmentiMAP", "TreatmentiMAP:time6"]
)

# SE for (β1 + β5)
se_12 <- sqrt(
  vcov_mat["TreatmentiMAP", "TreatmentiMAP"] +
  vcov_mat["TreatmentiMAP:time12", "TreatmentiMAP:time12"] +
  2 * vcov_mat["TreatmentiMAP", "TreatmentiMAP:time12"]
)

# --- Calculate odds ratios (OR), 99% confidence intervals, Wald z-statistics, and p-values ---

# OR and CI at 6 months
or_6 <- exp(beta1 + beta4)
ci_6 <- exp(c((beta1 + beta4) - 2.576 * se_6, (beta1 + beta4) + 2.576 * se_6))
z_6 <- (beta1 + beta4) / se_6
p_6 <- 2 * (1 - pnorm(abs(z_6)))

# OR and CI at 12 months
or_12 <- exp(beta1 + beta5)
ci_12 <- exp(c((beta1 + beta5) - 2.576 * se_12, (beta1 + beta5) + 2.576 * se_12))
z_12 <- (beta1 + beta5) / se_12
p_12 <- 2 * (1 - pnorm(abs(z_12)))

# --- Output the results as a named list ---
list(
  OR_6m = or_6,
  CI_6m = ci_6,
  z_6m = z_6,
  p_6m = p_6,
  
  OR_12m = or_12,
  CI_12m = ci_12,
  z_12m = z_12,
  p_12m = p_12
)

```

```{r}
# --- Create summary table ---
result_table <- data.frame(
  Time = c("6 months", "12 months"),
  OR = c(or_6, or_12),
  CI_Lower = c(ci_6[1], ci_12[1]),
  CI_Upper = c(ci_6[2], ci_12[2]),
  Wald_Z = c(z_6, z_12),
  P_Value = c(p_6, p_12)
)

# Display table
print(result_table)
```

```{r}
library(ggplot2)

plot_df <- data.frame(
  Time = c("6 Months", "12 Months"),
  OR = c(0.5876, 0.3733),
  CI_lower = c(0.2868, 0.1734),
  CI_upper = c(1.2038, 0.8037)
)

ggplot(plot_df, aes(x = Time, y = OR)) +
  geom_point(size = 3, color = "blue") +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2, color = "gray40") +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  coord_flip() +
  ylim(0, 1.3) +
  labs(
    title = "Odds Ratio of Suboptimal Dosing (iMAP vs. Standard Care)",
    y = "Odds Ratio (99% CI)",
    x = ""
  ) +
  theme_minimal(base_size = 13)

```

### Medication monitoring needed modeling
```{r}
model_medmon <- glmer(
  Med_Mon ~ Treatment * time + site + race + Med_Mon_0 + (1 | ID),
  data = long_df_analysis,
  family = binomial(link = "logit")
)

summary(model_medmon)
```

```{r}
# Extract model coefficients (log-odds)
coefs <- fixef(model_medmon)

# Extract variance-covariance matrix for fixed effects
vcov_mat <- vcov(model_medmon)

# Get key coefficients
# β₁: Main effect of iMAP at baseline
beta1 <- coefs["TreatmentiMAP"]

# β₄: Interaction (iMAP × time = 6)
beta4 <- coefs["TreatmentiMAP:time6"]

# β₅: Interaction (iMAP × time = 12)
beta5 <- coefs["TreatmentiMAP:time12"]

# Compute standard errors using delta method
# SE for β₁ + β₄
se_6 <- sqrt(
  vcov_mat["TreatmentiMAP", "TreatmentiMAP"] +
  vcov_mat["TreatmentiMAP:time6", "TreatmentiMAP:time6"] +
  2 * vcov_mat["TreatmentiMAP", "TreatmentiMAP:time6"]
)

# SE for β₁ + β₅
se_12 <- sqrt(
  vcov_mat["TreatmentiMAP", "TreatmentiMAP"] +
  vcov_mat["TreatmentiMAP:time12", "TreatmentiMAP:time12"] +
  2 * vcov_mat["TreatmentiMAP", "TreatmentiMAP:time12"]
)

# Compute odds ratios (OR), 99% confidence intervals, z-values, and p-values

# OR @ 6 months
or_6 <- exp(beta1 + beta4)
ci_6 <- exp(c((beta1 + beta4) - 2.576 * se_6, (beta1 + beta4) + 2.576 * se_6))
z_6 <- (beta1 + beta4) / se_6
p_6 <- 2 * (1 - pnorm(abs(z_6)))

# OR @ 12 months
or_12 <- exp(beta1 + beta5)
ci_12 <- exp(c((beta1 + beta5) - 2.576 * se_12, (beta1 + beta5) + 2.576 * se_12))
z_12 <- (beta1 + beta5) / se_12
p_12 <- 2 * (1 - pnorm(abs(z_12)))

# Output the results
list(
  OR_6m = or_6,
  CI_6m = ci_6,
  z_6m = z_6,
  p_6m = p_6,
  
  OR_12m = or_12,
  CI_12m = ci_12,
  z_12m = z_12,
  p_12m = p_12
)

```
```{r}
# --- Create summary table ---
result_table <- data.frame(
  Time = c("6 months", "12 months"),
  OR = c(or_6, or_12),
  CI_Lower = c(ci_6[1], ci_12[1]),
  CI_Upper = c(ci_6[2], ci_12[2]),
  Wald_Z = c(z_6, z_12),
  P_Value = c(p_6, p_12)
)

# Display table
print(result_table)
```

```{r}
# Input the OR and 99% CI values for iMAP vs SC
plot_df <- data.frame(
  Time = c("6 Months", "12 Months"),
  OR = c(0.9715561, 0.8608350),
  CI_lower = c(0.4917639, 0.4157322),
  CI_upper = c(1.919460, 1.782486)
)

# Create the plot
ggplot(plot_df, aes(x = Time, y = OR)) +
  geom_point(size = 3, color = "blue") +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2, color = "gray40") +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  coord_flip() +
  ylim(0, 2.0) +
  labs(
    title = "Odds Ratio of Medication Monitoring Needed (iMAP vs. Standard Care)",
    y = "Odds Ratio (99% CI)",
    x = ""
  ) +
  theme_minimal(base_size = 13)


```


### Suboptimal drug modeling

```{r}
# Sub_drug: GLMM with logit link
model_subdrug <- glmer(
  Sub_drug ~ Treatment * time + site + race + Sub_drug_0 + (1 | ID),
  data = long_df_analysis,
  family = binomial(link = "logit")
)

summary(model_subdrug)


```

```{r}
# Extract fixed effects and variance-covariance matrix
coefs <- fixef(model_subdrug)
vcov_mat <- vcov(model_subdrug)

# Coefficients for interaction
beta1 <- coefs["TreatmentiMAP"]
beta4 <- coefs["TreatmentiMAP:time6"]
beta5 <- coefs["TreatmentiMAP:time12"]

# Standard errors using delta method
se_6 <- sqrt(
  vcov_mat["TreatmentiMAP", "TreatmentiMAP"] +
  vcov_mat["TreatmentiMAP:time6", "TreatmentiMAP:time6"] +
  2 * vcov_mat["TreatmentiMAP", "TreatmentiMAP:time6"]
)

se_12 <- sqrt(
  vcov_mat["TreatmentiMAP", "TreatmentiMAP"] +
  vcov_mat["TreatmentiMAP:time12", "TreatmentiMAP:time12"] +
  2 * vcov_mat["TreatmentiMAP", "TreatmentiMAP:time12"]
)

# OR and 99% CI at 6 months
or_6 <- exp(beta1 + beta4)
ci_6 <- exp(c((beta1 + beta4) - 2.576 * se_6, (beta1 + beta4) + 2.576 * se_6))
z_6 <- (beta1 + beta4) / se_6
p_6 <- 2 * (1 - pnorm(abs(z_6)))

# OR and 99% CI at 12 months
or_12 <- exp(beta1 + beta5)
ci_12 <- exp(c((beta1 + beta5) - 2.576 * se_12, (beta1 + beta5) + 2.576 * se_12))
z_12 <- (beta1 + beta5) / se_12
p_12 <- 2 * (1 - pnorm(abs(z_12)))

# Output results
list(
  OR_6m = or_6, CI_6m = ci_6, z_6m = z_6, p_6m = p_6,
  OR_12m = or_12, CI_12m = ci_12, z_12m = z_12, p_12m = p_12
)

```

```{r}
# --- Create summary table ---
result_table <- data.frame(
  Time = c("6 months", "12 months"),
  OR = c(or_6, or_12),
  CI_Lower = c(ci_6[1], ci_12[1]),
  CI_Upper = c(ci_6[2], ci_12[2]),
  Wald_Z = c(z_6, z_12),
  P_Value = c(p_6, p_12)
)

# Display table
print(result_table)
```

```{r}
# Updated OR and 99% CI values from output
plot_df <- data.frame(
  Time = c("6 Months", "12 Months"),
  OR = c(1.0183309, 0.5868606),
  CI_lower = c(0.4874686, 0.2777750),
  CI_upper = c(2.127312, 1.239872)
)

# Plot
ggplot(plot_df, aes(x = Time, y = OR)) +
  geom_point(size = 3, color = "blue") +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2, color = "gray40") +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  coord_flip() +
  ylim(0, 2.3) +
  labs(
    title = "Odds Ratio of Suboptimal Drug Choice (iMAP vs. Standard Care)",
    y = "Odds Ratio (99% CI)",
    x = ""
  ) +
  theme_minimal(base_size = 13)



```




### Undertreat modeling
```{r}
# GLMM with logit link
model_under <- glmer(
  Undertreat ~ Treatment * time + site + race + Undertreat_0 + (1 | ID),
  data = long_df_analysis,
  family = binomial(link = "logit")
)

summary(model_under)
```


```{r}
coefs <- fixef(model_under)
vcov_mat <- vcov(model_under)

beta1 <- coefs["TreatmentiMAP"]
beta4 <- coefs["TreatmentiMAP:time6"]
beta5 <- coefs["TreatmentiMAP:time12"]

se_6 <- sqrt(
  vcov_mat["TreatmentiMAP", "TreatmentiMAP"] +
  vcov_mat["TreatmentiMAP:time6", "TreatmentiMAP:time6"] +
  2 * vcov_mat["TreatmentiMAP", "TreatmentiMAP:time6"]
)

se_12 <- sqrt(
  vcov_mat["TreatmentiMAP", "TreatmentiMAP"] +
  vcov_mat["TreatmentiMAP:time12", "TreatmentiMAP:time12"] +
  2 * vcov_mat["TreatmentiMAP", "TreatmentiMAP:time12"]
)


# Compute OR, 99% CI, z-value, and p-value for 6 and 12 months
# 6 months
or_6 <- exp(beta1 + beta4)
ci_6 <- exp(c((beta1 + beta4) - 2.576 * se_6, (beta1 + beta4) + 2.576 * se_6))
z_6 <- (beta1 + beta4) / se_6
p_6 <- 2 * (1 - pnorm(abs(z_6)))

# 12 months
or_12 <- exp(beta1 + beta5)
ci_12 <- exp(c((beta1 + beta5) - 2.576 * se_12, (beta1 + beta5) + 2.576 * se_12))
z_12 <- (beta1 + beta5) / se_12
p_12 <- 2 * (1 - pnorm(abs(z_12)))


list(
  OR_6m = or_6, CI_6m = ci_6, z_6m = z_6, p_6m = p_6,
  OR_12m = or_12, CI_12m = ci_12, z_12m = z_12, p_12m = p_12
)

```

```{r}
# --- Create summary table ---
result_table <- data.frame(
  Time = c("6 months", "12 months"),
  OR = c(or_6, or_12),
  CI_Lower = c(ci_6[1], ci_12[1]),
  CI_Upper = c(ci_6[2], ci_12[2]),
  Wald_Z = c(z_6, z_12),
  P_Value = c(p_6, p_12)
)

# Display table
print(result_table)
```


```{r}
# Input OR and 99% CI values from the latest output
plot_df <- data.frame(
  Time = c("6 Months", "12 Months"),
  OR = c(0.5458593, 0.5059454),
  CI_lower = c(0.2624432, 0.2319192),
  CI_upper = c(1.135340, 1.103749)
)

# Plot forest plot
ggplot(plot_df, aes(x = Time, y = OR)) +
  geom_point(size = 3, color = "blue") +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2, color = "gray40") +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  coord_flip() +
  ylim(0, 1.2) +
  labs(
    title = "Odds Ratio of Undertreatment (iMAP vs. Standard Care)",
    y = "Odds Ratio (99% CI)",
    x = ""
  ) +
  theme_minimal(base_size = 13)

```



# Adverse Drug Event Modeling

```{r}
model_ae <- glmer(
  AE ~ Treatment * time + site + race + AE_0 + (1 | ID),
  data = long_df_analysis,
  family = binomial(link = "logit")
)

summary(model_ae)
```

```{r}
coefs <- fixef(model_ae)
vcov_mat <- vcov(model_ae)

beta1 <- coefs["TreatmentiMAP"]
beta4 <- coefs["TreatmentiMAP:time6"]
beta5 <- coefs["TreatmentiMAP:time12"]


se_6 <- sqrt(
  vcov_mat["TreatmentiMAP", "TreatmentiMAP"] +
  vcov_mat["TreatmentiMAP:time6", "TreatmentiMAP:time6"] +
  2 * vcov_mat["TreatmentiMAP", "TreatmentiMAP:time6"]
)

se_12 <- sqrt(
  vcov_mat["TreatmentiMAP", "TreatmentiMAP"] +
  vcov_mat["TreatmentiMAP:time12", "TreatmentiMAP:time12"] +
  2 * vcov_mat["TreatmentiMAP", "TreatmentiMAP:time12"]
)


# Compute OR, 99% CI, z-value, and p-value for 6 and 12 months
# 6 months
or_6 <- exp(beta1 + beta4)
ci_6 <- exp(c((beta1 + beta4) - 2.576 * se_6, (beta1 + beta4) + 2.576 * se_6))
z_6 <- (beta1 + beta4) / se_6
p_6 <- 2 * (1 - pnorm(abs(z_6)))

# 12 months
or_12 <- exp(beta1 + beta5)
ci_12 <- exp(c((beta1 + beta5) - 2.576 * se_12, (beta1 + beta5) + 2.576 * se_12))
z_12 <- (beta1 + beta5) / se_12
p_12 <- 2 * (1 - pnorm(abs(z_12)))

list(
  OR_6m = or_6, CI_6m = ci_6, z_6m = z_6, p_6m = p_6,
  OR_12m = or_12, CI_12m = ci_12, z_12m = z_12, p_12m = p_12
)

```

```{r}
# --- Create summary table ---
result_table <- data.frame(
  Time = c("6 months", "12 months"),
  OR = c(or_6, or_12),
  CI_Lower = c(ci_6[1], ci_12[1]),
  CI_Upper = c(ci_6[2], ci_12[2]),
  Wald_Z = c(z_6, z_12),
  P_Value = c(p_6, p_12)
)

# Display table
print(result_table)
```

```{r}
# Updated OR and 99% CI values from output
plot_df <- data.frame(
  Time = c("6 Months", "12 Months"),
  OR = c(1.684668, 0.562770),
  CI_lower = c(0.4597227, 0.1480401),
  CI_upper = c(6.173518, 2.139353)
)

ggplot(plot_df, aes(x = Time, y = OR)) +
  geom_point(size = 3, color = "blue") +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2, color = "gray40") +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  coord_flip() +
  ylim(0, 6.5) +
  labs(
    title = "Odds Ratio of Adverse Drug Events (iMAP vs. Standard Care)",
    y = "Odds Ratio (99% CI)",
    x = ""
  ) +
  theme_minimal(base_size = 13)

```


### Nonadherence modeling
```{r}
model_nonad <- glmer(
  NonAd ~ Treatment * time + site + race + NonAd_0 + (1 | ID),
  data = long_df_analysis,
  family = binomial(link = "logit")
)


summary(model_nonad)
```

```{r}
coefs <- fixef(model_nonad)
vcov_mat <- vcov(model_nonad)


beta1 <- coefs["TreatmentiMAP"]
beta4 <- coefs["TreatmentiMAP:time6"]
beta5 <- coefs["TreatmentiMAP:time12"]

se_6 <- sqrt(
  vcov_mat["TreatmentiMAP", "TreatmentiMAP"] +
  vcov_mat["TreatmentiMAP:time6", "TreatmentiMAP:time6"] +
  2 * vcov_mat["TreatmentiMAP", "TreatmentiMAP:time6"]
)

se_12 <- sqrt(
  vcov_mat["TreatmentiMAP", "TreatmentiMAP"] +
  vcov_mat["TreatmentiMAP:time12", "TreatmentiMAP:time12"] +
  2 * vcov_mat["TreatmentiMAP", "TreatmentiMAP:time12"]
)

# Compute OR, 99% CI, z-value, and p-value for 6 and 12 months
# 6 months
or_6 <- exp(beta1 + beta4)
ci_6 <- exp(c((beta1 + beta4) - 2.576 * se_6, (beta1 + beta4) + 2.576 * se_6))
z_6 <- (beta1 + beta4) / se_6
p_6 <- 2 * (1 - pnorm(abs(z_6)))

# 12 months
or_12 <- exp(beta1 + beta5)
ci_12 <- exp(c((beta1 + beta5) - 2.576 * se_12, (beta1 + beta5) + 2.576 * se_12))
z_12 <- (beta1 + beta5) / se_12
p_12 <- 2 * (1 - pnorm(abs(z_12)))

list(
  OR_6m = or_6, CI_6m = ci_6, z_6m = z_6, p_6m = p_6,
  OR_12m = or_12, CI_12m = ci_12, z_12m = z_12, p_12m = p_12
)
```

```{r}
# --- Create summary table ---
result_table <- data.frame(
  Time = c("6 months", "12 months"),
  OR = c(or_6, or_12),
  CI_Lower = c(ci_6[1], ci_12[1]),
  CI_Upper = c(ci_6[2], ci_12[2]),
  Wald_Z = c(z_6, z_12),
  P_Value = c(p_6, p_12)
)

# Display table
print(result_table)
```

```{r}
# Updated OR and 99% CI values for Nonadherence
plot_df <- data.frame(
  Time = c("6 Months", "12 Months"),
  OR = c(0.9716208, 1.3834279),
  CI_lower = c(0.3320951, 0.4030767),
  CI_upper = c(2.842700, 4.748160)
)

ggplot(plot_df, aes(x = Time, y = OR)) +
  geom_point(size = 3, color = "blue") +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper),
                width = 0.2, color = "gray40") +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  coord_flip() +
  ylim(0, 5) +
  labs(
    title = "Odds Ratio of Nonadherence (iMAP vs. Standard Care)",
    y = "Odds Ratio (99% CI)",
    x = ""
  ) +
  theme_minimal(base_size = 13)


```

